Verifying Demonstrations

### 2018-05-24 paper/analysis-security.tex
Writes up sec analysis of temporal; updates linkability, designated
Spatial left to do.

\paragraph{Temporal eligibility, created after start}

\daniel{Rewrite this paragraph, do proper analysis.}
Given the properties of the storage (in \cref{StorageProperties}), for 
\cref{CreatedAfterStart}, each witness must include the hash value of an 
existing block in the blockchain in each proof share (shown as \(t_s\) in 
\cref{fig:ProofFig}).
Then it is clear that the proof must have been created after that block (since 
predicting such a value is hard).
This value can either be provided to the witness by the protester or the witness 
uses the value of the last known block.

\paragraph{Location proofs and spatial eligibility}

@@

\paragraph{Temporal eligibility, created before end}

The proofs are committed to the blockchain, thus they cannot have been created 
after.
\daniel{Do a proper security analysis.}

\paragraph{Linkability and designated protest}

\Cref{CountOnce} is required to prevent Sybil attacks, \ie that one individual 
can provide two participation proofs and thus be counted twice.
This is prevented by the use of \(\pid\).
To be counted twice, Alice must produce a \(\pid'\neq \pid\) and two signatures:
\begin{multline*}
\pi_{\pid'} = \SPK\mleft\{ (\sk_P') : \mright. \\
  \begin{aligned}
    \pid' &= \ACprf[_{\sk_P'}][\cid], \\
    \sigma_P'' &= \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
  \end{aligned} \\
    (\cid, \pid', \wid', t_s, t_s', l, \wsig')
\end{multline*}
and
\begin{multline*}
  \pi_{\wid', \wsig'}\gets \SPK\left\{ (\sk_W') : \right. \\
    \begin{aligned}
      \wid' &= \ACprf[_{\sk_W'}][\pid'] \quad \land \\
      \wsig' &= \ACprf[_{\sk_W'}][\wid', t_s, t_s', l] \quad \land \\
      \sigma_W'' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W']] \right\}
    \end{aligned} \\
      (\pid', \wid', t_s, t_s', l, \wsig').
\end{multline*}

\daniel{There are several approaches for Alice to do this, \eg attacking the 
  \(\SPK\)-signature, the \(\AC\)-signature, \etc.
  I think we should describe them.}

\Cref{DesignatedEvent} is to prevent Alice from reusing the same proof (or proof 
share) for another event --- or someone else using her proof-share for another 
event.
This is done with the use of \(\cid\) in the proof shares.
Thus to reuse the proof share for another protest, with a different manifesto, 
one must find a second preimage \(\mfst'\) such that \(\cid = \Hash[\mfst] = 
  \Hash[\mfst']\).

>>>>

\paragraph{Temporal eligibility}%
\label{analysis-temporal}

\Cref{TemporallyRelated} ensures freshness, \ie that we cannot simply resubmit 
an old proof as a new one.
In general, freshness requires the prover to respond to an unpredictable 
challenge.
The challenge here is to include the hash value at the head of the blockchain at 
the time of the proof's creation (included as \(t_s\) and \(t_s'\) in the proof 
share).
As per construction of blockchains, the hash value at the head depends on the 
previous blocks in the chain.
Thus the predictability of \(t_s\) depends on the predictability of the blocks, 
which depends on the predictability of the transactions and the nonce needed by 
the miner.
The transactions in turn depend on the signatures made by the signing keys 
corresponding to the used transactions.
If these were predictable, our adversary could spend arbitrary transactions in 
the blockchain --- which is designed to be hard.
Thus Alice can predict \(t_s\) with negligible probability, \ie \(t_s\) must 
have been published on the blockchain before being included in her proof share.

According to \cref{TemporallyRelated}, we must also prove that a proof share has 
not been created after a certain time.
The hash values of the proof shares are committed to the blockchain, thus there 
is a negligible probability that they were created after that.
Alice would have to choose a value \(y\) in the domain of the hash function 
\(\Hash\) and then find a preimage \(x\) such that \(y = \Hash[x]\) and \(x\) is 
a valid proof.
If \(\Hash\) is collision resistant, then finding \emph{any} preimage is hard.

\paragraph{Spatial eligibility}%
\label{analysis-spatial}

@@

\paragraph{Linkability}%
\label{analysis-linkability}

\Cref{CountOnce} is required to prevent Sybil attacks, \ie that one individual 
can provide two participation proofs and thus be counted twice.
This is prevented by the use of \(\pid\).
To be counted twice, Alice must produce a \(\pid'\neq \pid\).
Due to the deterministic property of \(\ACprf\), Alice must produce a new key 
\(\sk_P'\) and make the witness accept in the protocol
\begin{multline*}
\PK\mleft\{ (\sk_P') : \pid' = \ACprf[_{\sk_P'}][\cid], \mright. \\
    \sigma_P'' = \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
\end{multline*}
while she does not know a valid signature on \(\sk_P'\).
This is thus reduced to the security of the \(\AC\) scheme and how often Alice 
can get a valid signature on a secret key from the \ac{CA}.

\paragraph{Designated protest}%
\label{analysis-designated}

\Cref{DesignatedEvent} is to prevent Alice from reusing the same proof (or proof 
share) for another event --- or someone else using her proof-share for another 
event.
This is prevented with the use of \(\cid\) in the proof shares.
Thus to reuse the proof share for another protest, with a different manifesto, 
one must find a second preimage \(\mfst'\) such that \(\cid = \Hash[\mfst] = 
  \Hash[\mfst']\).

\paragraph{Forging proof shares}

\daniel{This is work-in-progress.}
Alice can attempt to forge the full proof directly, \ie
\begin{multline*}
\pi_{\pid'} = \SPK\mleft\{ (\sk_P') : \mright. \\
  \begin{aligned}
    \pid' &= \ACprf[_{\sk_P'}][\cid], \\
    \sigma_P'' &= \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
  \end{aligned} \\
    (\cid, \pid', \wid', t_s, t_s', l, \wsig')
\end{multline*}
and consequently
\begin{multline*}
  \pi_{\wid', \wsig'}\gets \SPK\left\{ (\sk_W') : \right. \\
    \begin{aligned}
      \wid' &= \ACprf[_{\sk_W'}][\pid'] \quad \land \\
      \wsig' &= \ACprf[_{\sk_W'}][\wid', t_s, t_s', l] \quad \land \\
      \sigma_W'' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W']] \right\}
    \end{aligned} \\
      (\pid', \wid', t_s, t_s', l, \wsig'),
\end{multline*}
and thus solve same problem twice (once for \(pid'\) and once for \(\wid'\)).

### 2018-05-24 paper/properties.tex
Writes up sec analysis of temporal; updates linkability, designated
Spatial left to do.

To define these properties more formally in the context of protest, we desire three verifiability requirements, among which eligibility can be further broken up in four subproperties:
\begin{requirements}[V]
  \item\label{EligibilityVerif} \emph{Eligibility}:
    anyone can verify that each participation proof provides temporal and 
    spatial eligibility and that only one participation proof is counted per 
    individual.
    \begin{requirements}
    \item\label{CreatedAfterStart} \emph{Temporal eligibility}:
      prove that the proof was created after the start of the protest and
      %\label{CreatedBeforeEnd} prove that the proof was created 
      before the end of the protest.
    \item\label{SpatiallyRelated} \emph{Spatial eligibility}:
      prove that the proof is spatially related to the physical location or 
      journey of the protest.
    \item\label{CountOnce} \emph{One-proof-per-person}:
      prove that no individual can be counted more than once for a particular 
      protest.
    \item\label{DesignatedEvent} \emph{Designated event}:
      prove that the proof is designated for the protest.
    \end{requirements}

>>>>

To define these properties more formally in the context of protest, we desire three verifiability requirements, among which eligibility can be further broken up in four subproperties:
\begin{requirements}[V]
  \item\label{EligibilityVerif} \emph{Eligibility}:
    anyone can verify that each participation proof provides temporal and 
    spatial eligibility and that only one participation proof is counted per 
    individual.
    \begin{requirements}
    \item\label{TemporallyRelated} \emph{Temporal eligibility}:
      prove that the proof was created after the start of the protest and
      before the end of the protest.
    \item\label{SpatiallyRelated} \emph{Spatial eligibility}:
      prove that the proof is spatially related to the physical location or 
      journey of the protest.
    \item\label{CountOnce} \emph{One-proof-per-person}:
      prove that no individual can be counted more than once for a particular 
      protest.
    \item\label{DesignatedEvent} \emph{Designated event}:
      prove that the proof is designated for the protest.
    \end{requirements}
